When the robot considers the human...

### 2013-04-23 paper.tex
Updated several figures
Updated style for Journal of Artificial Intelligence

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx, subfigure}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{fixme}
\usepackage{lscape}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

@@

\begin{document}

\title*{When the robot considers the human... }
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Rachid Alami, Mathieu Warnier, Julien Guitton, S\'{e}verin Lemaignan and Emrah Akin Sisbot}
\authorrunning{R. Alami, M. Warnier, J. Guitton, S. Lemaignan and E.A. Sisbot}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{ LAAS-CNRS\\ 
        Universit\'e de Toulouse, UPS, INSA, INP, ISAE, LAAS\\ 
         F-31077 Toulouse, France\\ \email{Firstname.Name@laas.fr}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{This paper addresses some key decisional issues that are
  necessary for a cognitive robot which shares space and tasks with a
  human. We adopt a constructive approach based on the identification
  and the effective implementation of individual and collaborative
  skills. The system is comprehensive since it aims at dealing with a
  complete set of abilities articulated so that the robot controller
  is effectively able to conduct in a flexible manner a collaborative
  task with a human partner. These abilities include geometric
  reasoning and situation assessment based essentially on
  perspective-taking and affordances, management and exploitation of
  each agent (human and robot) knowledge in a separate cognitive
  model, human-aware task planning and human and robot interleaved
  plan achievement.}

\abstract{This paper addresses some key decisional issues that are
  necessary for a cognitive robot which shares space and tasks with a
  human. We adopt a constructive approach based on the identification
  and the effective implementation of individual and collaborative
  skills. The system is comprehensive since it aims at dealing with a
  complete set of abilities articulated so that the robot controller
  is effectively able to conduct in a flexible manner a collaborative
  task with a human partner. These abilities include geometric
  reasoning and situation assessment based essentially on
  perspective-taking and affordances, management and exploitation of
  each agent (human and robot) knowledge in a separate cognitive
  model, human-aware task planning and human and robot interleaved
  plan achievement.}

@@

\begin{figure*}[thpb]
  \centering
  \includegraphics[width=1.0\textwidth]{./figs/supervisor-architecture-new.pdf} \\
  \caption {Architecture of the robot control system}
  \label{architecture_fg}
\end{figure*}

@@

% \begin{landscape}
% \begin{figure*}[thpb]
%   \centering
% %  \includegraphics[width=1.0\textwidth]{./figs/manip_run.pdf} \\
%   \includegraphics[width=17cm]{./figs/manip_run.pdf} \\
% \begin{center}
%   \caption {An example of a human-robot collaborative goal achievement}
% \end{center}
%   \label{manip_run_fg}
% \end{figure*}
% \end{landscape}

\begin{figure*}[thpb]
  \centering
\includegraphics[width=1.0\textwidth]{./figs/rotated-rachid_manip_run-v2.pdf} \\
%  \includegraphics[width=17cm]{./figs/manip_run-vertical.pdf} \\
\begin{center}
  \caption {An example of a human-robot collaborative goal achievement}
\end{center}
  \label{manip_run_fg}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{alpha}
\bibliographystyle{plain}
\bibliography{laas_hri}
%% \end{thebibliography}

>>>>

\documentclass{elsarticle}

\usepackage{graphicx, subfigure}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{url}
\usepackage{fixme}
\usepackage{lscape}

\journal{Journal of Artificial Intelligence}

@@

\begin{document}
\begin{frontmatter}

\title{When the robot considers the human... }
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Rachid Alami, Mathieu Warnier, Julien Guitton, S\'{e}verin Lemaignan and Emrah Akin Sisbot}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\address{ LAAS-CNRS\\ 
        Universit\'e de Toulouse, UPS, INSA, INP, ISAE, LAAS\\ 
         F-31077 Toulouse, France\\ \texttt{Firstname.Name@laas.fr}}

\begin{abstract}
  This paper addresses some key decisional issues that are
  necessary for a cognitive robot which shares space and tasks with a
  human. We adopt a constructive approach based on the identification
  and the effective implementation of individual and collaborative
  skills. The system is comprehensive since it aims at dealing with a
  complete set of abilities articulated so that the robot controller
  is effectively able to conduct in a flexible manner a collaborative
  task with a human partner. These abilities include geometric
  reasoning and situation assessment based essentially on
  perspective-taking and affordances, management and exploitation of
  each agent (human and robot) knowledge in a separate cognitive
  model, human-aware task planning and human and robot interleaved
  plan achievement.
\end{abstract}

\begin{keyword}
    %% keywords here, in the form: keyword \sep keyword

    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

@@

\begin{figure*}[thpb]
  \centering
  \includegraphics[width=1.0\textwidth]{./figs/archi.pdf} \\
  \caption {Architecture of the robot control system}
  \label{architecture_fg}
\end{figure*}

@@

\begin{figure*}[thpb]
  \centering
    \includegraphics[width=1.0\textwidth]{./figs/manip_run.pdf} \\
    \begin{center}
    \caption {An example of a human-robot collaborative goal achievement}
    \end{center}
  \label{manip_run_fg}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{elsarticle-num}
\bibliography{laas_hri}
